---
title: "analysis"
date: "8/23/2019"
output: html_document
---

## Setup

```{r setup}
library(tidyverse)
library(ggridges)
library(pwr) 
library(grid)
library(gtable)

library(boot)
library(bootES)


library(ggbeeswarm)

library(tidybayes)
library(cowplot)
library(broom)

theme_set(theme_tidybayes() + panel_border() + background_grid())


#df <- read.csv("../results/pilot/CSV/TidyR.csv")
df <- read.csv("../results/study/CSV/TidyR.csv")
dfp <- read.csv("../results/study/CSV/participantInfoTidyR.csv")
```


## Data Cleaning / Types

```{r}

df_acc <- df %>% 
  filter(measure=="accuracy") 

df_acc$value = as.numeric( as.character(df_acc$value ))


df_acc
```

## Quick Check Charts

95% CIs + jitter (don't trust those point positions)

```{r}

df %>% 
  filter(measure=="accuracy") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot( aes(x=taskId, y=value) ) +
    geom_jitter( alpha = 0.2, width=0.1, height=0.3 ) + 
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, position = position_nudge(x=0.25, y=0), alpha=0.5) +
  coord_flip() +
    facet_grid(. ~ visType)

df %>% 
  filter(measure=="accuracy") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot( aes(x=taskId, y=value) ) +
    geom_jitter( alpha = 0.2, width=0.1, height=0.3 ) + 
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, position = position_nudge(x=0.25, y=0), alpha=0.5) +
  coord_flip() +
    facet_grid(. ~ visType)

## beeswarm big chart
## ci plots with titles and new tidyr
## hypothesis column
## task centric and hypothesis centric charts
## time and difficulty and correctness and confidence
## confidence ellipse
## age education and gender
## compare to prior and pilot

```

we can do the same with distributions, ridges

```{r}
df %>% 
  filter(measure=="accuracy") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot( aes(x=value, y=taskId) ) +
    geom_density_ridges() +
    facet_grid(. ~ visType)

```


, and density plots (look meh-- could probably combine + color for a better look)

```{r, fig.height=10, fig.width=10}

df %>% 
  filter(measure=="accuracy") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot( aes(value) ) +
    geom_density( alpha = 0.2 ) +
    facet_grid(taskId ~ visType)

```


## Power Analysis

```{r}

powerAnalysisGraph <- function(m1, m2, stdev, iterNum=15){
  # stdev <- sd_duration.median
  # m1 <- mean(search$duration.median)
  # m2 <- mean(nonsearch$duration.median)
  # # m1 <- mean(foresight$duration.median)
  # # m2 <- mean(nonsearch$duration.median)
  
  iteration <- 15
  
  difference <- 0
  effectSize <- 0
  numParticipants <- 0
  
  for(step in 1:iteration)
  {
    difference[step] <- abs(m1 - m2) * (0.9 ^ (step-1))
    effectSize[step] <- difference[step] / stdev
    numParticipants[step] <- pwr.t.test( 
      d=effectSize[step], 
      sig.level=.05, 
      power=0.8, 
      type="two.sample", 
      alternative="greater" 
    )$n * 1.15 * 2
  }
  
  #dual axis code online: https://rpubs.com/kohske/dual_axis_in_ggplot2
  grid.newpage()
  
  pw <- data.frame(difference=difference, numParticipants=numParticipants, effectSize=effectSize)
  p1 <- ggplot(pw,aes(x=difference)) + geom_line(aes(y = numParticipants)) +
    scale_y_continuous(breaks = pretty(pw$numParticipants, n = 10))
  p2<- ggplot(pw,aes(x=difference)) + geom_line(aes(y = effectSize)) +
    theme(panel.background = element_rect(fill = NA))+
    scale_y_continuous(breaks = pretty(pw$effectSize, n = 10))
  p2
  
  # extract gtable
  g1 <- ggplot_gtable(ggplot_build(p1))
  g2 <- ggplot_gtable(ggplot_build(p2))
  
  # overlap the panel of 2nd plot on that of 1st plot
  pp <- c(subset(g1$layout, name == "panel", se = t:r))
  g <- gtable_add_grob(g1, g2$grobs[[which(g2$layout$name == "panel")]], pp$t, pp$l, pp$b, pp$l)
  
  # axis tweaks
  ia <- which(g2$layout$name == "axis-l")
  ga <- g2$grobs[[ia]]
  ax <- ga$children[[2]]
  ax$widths <- rev(ax$widths)
  ax$grobs <- rev(ax$grobs)
  ax$grobs[[1]]$x <- ax$grobs[[1]]$x - unit(1, "npc") + unit(0.15, "cm")
  g <- gtable_add_cols(g, g2$widths[g2$layout[ia, ]$l], length(g$widths) - 1)
  g <- gtable_add_grob(g, ax, pp$t, length(g$widths) - 1, pp$b)
  
  # draw it
  grid.draw(g)
}

```


then, we test it out with some parameters estimated by eye from our charts so far

```{r}
# task 8 (reading values from graph, could do exact later)
powerAnalysisGraph(0.5, 0.6, 0.25)

# task 13 (reading values from graph, could do exact later)
powerAnalysisGraph(0.2, 0.4, 0.10)
```

Now we want to get better estimates for parameters.
We need Means from each group, on each task, and a pooled stdev.

```{r}

# task 08
sd_t08 = df_acc %>% 
  filter(taskId == "S-task08") %>% 
  summarise(
    stdev = sd(value)
  )

m_nl_t08 = df_acc %>% 
  filter(taskId == "S-task08" & visType == "nodeLink") %>% 
  summarise(
    mean = mean(value)
  )

m_adj_t08 = df_acc %>% 
  filter(taskId == "S-task08" & visType == "adjMatrix") %>% 
  summarise(
    mean = mean(value)
  )

# task 13
sd_t13 = df_acc %>% 
  filter(taskId == "S-task13") %>% 
  summarise(
    stdev = sd(value)
  )

m_nl_t13 = df_acc %>% 
  filter(taskId == "S-task13" & visType == "nodeLink") %>% 
  summarise(
    mean = mean(value)
  )

m_adj_t13 = df_acc %>% 
  filter(taskId == "S-task13" & visType == "adjMatrix") %>% 
  summarise(
    mean = mean(value)
  )

```
... and now some more accurate power analysis graphs

```{r}

powerAnalysisGraph(m_adj_t08[,1], m_nl_t08[,1], sd_t08[,1])

powerAnalysisGraph(m_adj_t13[,1], m_nl_t13[,1], sd_t13[,1])

```



Interpreting the task 13 graph: 
"Given no changes in Means or pooled stdev, and assuming a t-test, you'd need ~225 people total to find a medium effect size."


## Rank-style tests

Given the data isn't technically continuous at the measurement level, we might consider non-parametric tests:

```{r}
t13_nl = df_acc %>% 
  filter(taskId == "S-task13" & visType == "nodeLink")

t13_adj = df_acc %>% 
  filter(taskId == "S-task13" & visType == "adjMatrix")

# p = 0.06-- promising at the pilot level
wilcox.test(t13_nl$value, t13_adj$value)
```

```{r}
wtest <- function(task) {
t13_nl = df_acc %>% 
  filter(taskId == task & visType == "nodeLink")

t13_adj = df_acc %>% 
  filter(taskId == task & visType == "adjMatrix")

# p = 0.06-- promising at the pilot level
print(task)
wilcox.test(t13_nl$value, t13_adj$value)
}

wtest("S-task01")
wtest("S-task02")
wtest("S-task03")
wtest("S-task04")
wtest("S-task05")
wtest("S-task06")
wtest("S-task07")
wtest("S-task08")
wtest("S-task09")
wtest("S-task10")
wtest("S-task11")
wtest("S-task12")
wtest("S-task13")
wtest("S-task14")
wtest("S-task15")
wtest("S-task16")
```


## CIs

```{r, warning=FALSE}

# Bootstrap 95% CI for mean
# function to obtain mean from the data (with indexing)
mean.fun <- function(D, d) {
  return( mean(D[d]) )
}

reportCI <- function(data, attr) {
  # bootstrapping with 1000 replications
  ci <- boot.ci(
    boot(data=data[[attr]], statistic=mean.fun, R=1000, sim="ordinary")
  )

  cat( "M=",     round( mean( data[[attr]] ), 2), "~",
       "[", round( ci$bca[,4]          , 2), ",",
       round( ci$bca[,5]          , 2), "]",
       sep="")
}

citext <- function(task, measure_) {
  
df_tmp <- df %>% 
  filter(measure==measure_) 

df_tmp$value = as.numeric( as.character(df_tmp$value ))

nl = df_tmp %>% 
  filter(taskId == task & visType == "nodeLink")

adj = df_tmp %>% 
  filter(taskId == task & visType == "adjMatrix")

cat( paste(task," | node link\n") )
reportCI(nl, "value")
cat( "\n" )


cat( paste(task," | adj matrix\n") )
reportCI(adj, "value")
cat( "\n" )
cat( "\n" )


}
# cat("\n\n =========ACCURACIES======== \n\n")
# 
# citext("S-task01", "accuracy")
# citext("S-task02", "accuracy")
# citext("S-task03", "accuracy")
# citext("S-task04", "accuracy")
# citext("S-task05", "accuracy")
# citext("S-task06", "accuracy")
# citext("S-task07", "accuracy")
# citext("S-task08", "accuracy")
# citext("S-task09", "accuracy")
# citext("S-task10", "accuracy")
# citext("S-task11", "accuracy")
# citext("S-task12", "accuracy")
# citext("S-task12A", "accuracy")
# citext("S-task12B", "accuracy")
# citext("S-task13", "accuracy")
# citext("S-task14", "accuracy")
# citext("S-task15", "accuracy")
# #citext("S-task16", "accuracy")
# 
 cat("\n\n =========TIMES======== \n\n")
# 
# citext("S-task01", "minutesOnTask")
# citext("S-task02", "minutesOnTask")
# citext("S-task03", "minutesOnTask")
# citext("S-task04", "minutesOnTask")
# citext("S-task05", "minutesOnTask")
# citext("S-task06", "minutesOnTask")
# citext("S-task07", "minutesOnTask")
# citext("S-task08", "minutesOnTask")
# citext("S-task09", "minutesOnTask")
# citext("S-task10", "minutesOnTask")
# citext("S-task11", "minutesOnTask")
# citext("S-task12", "minutesOnTask")
# citext("S-task13", "minutesOnTask")
# citext("S-task14", "minutesOnTask")
# citext("S-task15", "minutesOnTask")
# citext("S-task16", "minutesOnTask")


for (task in seq(1,16,1)){
  citext(paste("S-task", sprintf("%.2d",task),sep=""),"minutesOnTask")

}

# cat("\n\n =========DIFFICULTY======== \n\n")
# for (task in seq(1,16,1)){
#   citext(paste("S-task", sprintf("%.2d",task),sep=""),"difficulty")
# 
# }
# 
# cat("\n\n =========CONFIDENCE======== \n\n")
# for (task in seq(1,16,1)){
#     citext(paste("S-task", sprintf("%.2d",task),sep=""),"confidence")
# 
# }


```


## Effect Sizes

Note: at least as of 10-Sep-2019, negative effect sizes appear to mean "the adjMatrix wins" aka the adjMatrix has a higher accuracy

```{r, warning=FALSE}


reportES <- function(data, attr, group) {

  lvs <- levels(data[[group]])

  b <- bootES(data,
              data.col=attr,
              group.col=group,
              contrast=lvs, # normal cases c(group1=1, group2=-1), but for 2 groups, it's simplified.
              effect.type="cohens.d")

  cat( "d=", round( b$t0, 2), "~",
       "[", round( b$bounds[1], 2), ",",
       round( b$bounds[2], 2), "]",
       sep="")
}

estext <- function(task, measure_) {
  
df_tmp <- df %>% 
  filter(measure==measure_) 

df_tmp$value = as.numeric( as.character(df_tmp$value ))

esd = df_tmp %>% 
  filter(taskId == task)

cat( paste(task, "\n") )
reportES(esd, "value", "visType")
cat( "\n" )
cat( "\n" )


}
cat("\n\n =========ACCURACIES======== \n\n")

estext("S-task01", "accuracy")
estext("S-task02", "accuracy")
estext("S-task03", "accuracy")
estext("S-task04", "accuracy")
estext("S-task05", "accuracy")
estext("S-task06", "accuracy")
estext("S-task07", "accuracy")
estext("S-task08", "accuracy")
estext("S-task09", "accuracy")
estext("S-task10", "accuracy")
estext("S-task11", "accuracy")
estext("S-task12", "accuracy")
estext("S-task13", "accuracy")
estext("S-task14", "accuracy")
estext("S-task15", "accuracy")
#estext("S-task16", "accuracy")

cat("\n\n =========TIMES======== \n\n")

estext("S-task01", "minutesOnTask")
estext("S-task02", "minutesOnTask")
estext("S-task03", "minutesOnTask")
estext("S-task04", "minutesOnTask")
estext("S-task05", "minutesOnTask")
estext("S-task06", "minutesOnTask")
estext("S-task07", "minutesOnTask")
estext("S-task08", "minutesOnTask")
estext("S-task09", "minutesOnTask")
estext("S-task10", "minutesOnTask")
estext("S-task11", "minutesOnTask")
estext("S-task12", "minutesOnTask")
estext("S-task13", "minutesOnTask")
estext("S-task14", "minutesOnTask")
estext("S-task15", "minutesOnTask")
estext("S-task16", "minutesOnTask")
```

## TODO Subtract CIs?

## TODO Tidybayes-style eye plots (in progress + may be abandoned)

```{r}
# df %>% 
#   filter(measure=="accuracy") %>% 
#   mutate( value = as.numeric(value) ) %>% 
#   ggplot( aes(x=taskId, dist="norm", arg1=value) ) +
#   geom_halfeyeh() +
  


m_acc = lm(value ~ taskId, data = df_acc)

summary(m_acc)

tidy(m_acc)

m_acc %>%
  tidy() %>%
  ggplot() +
  geom_halfeyeh( aes(x=term, y=estimate)) 


```


## Participant Info

```{r}
fct_unique(dfp$measure)

dfp %>% 
  filter(measure == "age") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot() +
    geom_density( aes(x=value), fill="blue", alpha=0.75 ) 

dfp %>% 
  filter(measure == "age") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot(aes(x="age", y=value)) +
    geom_beeswarm(priority='random',cex=2, alpha=0.6) +
  coord_flip() +
  xlab("") + ylab("")

```


## Task Beeswarms

```{r, fig.width=8, fig.height=2}

fct_unique(df$measure)

# TODO scales fix for each measure (make global plot and use to fix scales)... but have to do for each measure!
# TODO color choices could be better
# TODO figure width and height?
# TODO manual order for measures?

vplot <- function(task) {

sdf = df %>% filter( taskId == task )
tt = as.character(sdf[1,]$taskTitle)

df %>% 
  filter( measure == "accuracy" | measure == "minutesToComplete" | 
            measure == "difficulty" | measure == "confidence") %>% 
    filter( taskId == task ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot(aes(x=visType, y=value, fill=visType, color=visType)) +
    facet_wrap(. ~ measure, scales="free", nrow=1) +
    geom_violin() +
    stat_summary(fun.data = "mean_cl_boot", colour = "green", size = 0.5, alpha=0.5) +
  coord_flip() + 
    labs(
      title = tt,
      subtitle = task
    )
  
ggsave(paste("violins/",task,".pdf", sep=""), width = 10, height = 2.5, units = "in")
}

vplot("S-task01")
vplot("S-task02")
vplot("S-task03")
vplot("S-task04")
vplot("S-task05")
vplot("S-task06")
vplot("S-task07")
vplot("S-task08")
vplot("S-task09")
vplot("S-task10")
vplot("S-task11")
vplot("S-task12")
vplot("S-task13")
vplot("S-task14")
vplot("S-task15")
vplot("S-task16")

```


## Beeswarm debugging


## Grouped Charts

T1/T2

T4/T5

T10/T11

T13/T14

```{r, fig.width=10, fig.height=6}

df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task01" | taskId == "S-task02" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task01_S-task02.pdf")

df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task04" | taskId == "S-task05" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task04_S-task05.pdf")


df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task10" | taskId == "S-task11" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task10_S-task11.pdf")

df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task13" | taskId == "S-task14" ) %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  mutate( condition = paste(taskId, visType, sep="_") ) %>% 
  ggplot(aes(x=condition, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.25  ) +
    stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 0.5, alpha=0.75) +
  coord_flip()

ggsave("comparisons/S-task13_S-task14.pdf")



```

## S-Task12 debugging

```{r}
df %>% 
  filter( measure == "accuracy" ) %>% 
  filter( taskId == "S-task12") %>% 
  mutate( value = as.numeric( as.character(value)) ) %>% 
  ggplot(aes(x=visType, y=value, fill=visType, color=visType)) +
  geom_jitter( alpha = 0.3, height=0.01, width=0.01  ) + 
  coord_flip()
```

